	
	\documentclass[10pt]{article}
	\usepackage{amssymb}
	\usepackage{hyperref}
	\usepackage{color}
	\usepackage{soul}
	\usepackage{fontawesome}
	\usepackage[document]{ragged2e}
	
	\DeclareFontFamily{U}{fontawesomeOne}{}
	\DeclareFontShape{U}{fontawesomeOne}{m}{n}
  		{<-> FontAwesome--fontawesomeone}{}
	\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}	
	
	\setlength{\headheight}{-0.8in}
	\setlength{\headsep}{-0.3in}
	\addtolength{\topmargin}{0.1in}
	%\setlength{\topskip}{0.8in}
	%\setlength{\topskip}{0.0in}
	%\setlength{\topskip}{-1.0in}
	%\setlength{\topskip}{-0.7in}
	%\setlength{\footskip}{-0.6in}
	%\setlength{\textheight}{10.0in}
	\setlength{\textheight}{11.0in}
	\setlength{\oddsidemargin}{0.0in}
	\setlength{\evensidemargin}{0.0in}
	\setlength{\textwidth}{6.8in}
	
	\clubpenalty 10000
	\widowpenalty 10000
	\sloppy
	
	\newcommand{\comment}[1]{}
	\renewcommand{\baselinestretch}{1.0}
	
	\begin{document}
	
	\raggedright
	
	\setlength{\parindent}{0.0in}
	
	\setlength{\leftmargini}{0.25in}
	\setlength{\leftmarginii}{0.25in}
	
	\newcommand{\heading}[1]{
	 \raggedright
	\begin{flushleft}
	 \vspace{0.02in}
	 {\sffamily\large\textsc{#1}}\\
	 \rule[0.115in]{6.8in}{0.01in}
	 \vspace{-0.365in}
	\end{flushleft}
	}
	\newcommand{\elskip}
	{\vspace*{0.03in}}
	
	\newcommand{\mins}
	{\vspace*{-0.1in}}
	
	\newcommand{\miniskip}
	{\vspace*{0.05in}}
	
	\newcommand{\header}{
	\raggedright
	\begin{flushleft}
	\parbox[c]{1.95in}{
	 \raggedright
	\begin{flushleft}
	Postdoctoral Fellow,\\
	Max Planck Institute\\
	for Human Development,\\
	Berlin, Germany.\\
	\end{flushleft}
	}
	\hfill
	\begin{minipage}[c]{2.25in}	
	 \begin{center}
	  { \Large \textsc{\textcolor{black}{Indrajeet Patil}}\\
	  \begin{small}
	  \miniskip
	  (\tt patilindrajeet.science@gmail.com)\\
	  \texttt{\today}
	  \end{small}}
	 \end{center}
	\end{minipage}
	\hfill
	\parbox[c]{1.8in}
	{
	\begin{flushright}
	\raggedleft
	 \href{https://goo.gl/ss7v6C}{\Huge \faGithub} ~~ \href{https://www.linkedin.com/in/indrajeet-patil-397865174/}{\Huge \faLinkedinSquare} ~~ \href{https://twitter.com/patilindrajeets}{\Huge \faTwitterSquare} ~~ \href{https://stackoverflow.com/users/7973626/indrajeet-patil}{\Huge \faStackOverflow} 
	\end{flushright}
	}
	
	%\miniskip\miniskip\miniskip
	\end{flushleft}
	\vspace*{-0.2in}
	}
	\newcommand{\smallheader}{
	 \begin{center}
	  {
	 \Large \textsc{Indrajeet S. Patil}}
	  \miniskip
	 \end{center}
	}
	\thispagestyle{empty}
	
	\header

	\heading{\textbf{Experience}}

	\begin{itemize}

    \itemsep-0.1em
	\item \textbf{\textcolor{blue}{Postdoctoral Fellow}}, \textcolor{black}{Max Planck Institute for Human Development}, Germany, 2019-.
	\miniskip
	
	\item \textbf{\textcolor{blue}{Postdoctoral Fellow}}, Department of Psychology, \textcolor{black}{Harvard University}, USA, 2017-2019.
	\vspace*{-0.09in}
	
	\begin{itemize}
	\itemsep-0.1em 
	\item[--] Designed a novel Reinforcement Learning paradigm to model human moral learning.	
	\item[--] Conducted a meta-analysis to dissociate the role of empathic concern versus distress in altruism.
	\end{itemize}
	\vspace*{-0.09in}

	\item \textbf{\textcolor{blue}{Ph.D. Researcher}}, Scuola Internazionale Superiore di Studi Avanzati (\textcolor{black}{SISSA}), Trieste, Italy, 2011-2015.
	\vspace*{-0.09in}

	\begin{itemize}
	\itemsep-0.1em 
	\item[--] Collected	and analyzed neuroimaging data to link moral decision-making and brain function.
	\item[--] Created novel Virtual Reality paradigms to study human moral \textit{behavior}.
	\item[--] Studied clinical deficits in autism, multiple sclerosis, and anxiety disorders.
	\end{itemize}
    \vspace*{-0.09in}
    
	\end{itemize}    
    
	\heading{\textbf{Technical Skills}}
	
	\begin{itemize}
	
	\item \textcolor{blue}{\textbf{Programming skills}}\\
     \vspace*{-0.09in}
     
    \begin{itemize}
    
    \itemsep-0.1em		
	\item[--] Data analysis: \textcolor{blue}{R} (advanced), \textcolor{blue}{MATLAB} (intermediate), \textcolor{blue}{Python} (beginner)
	\item[--] Database management: \textcolor{blue}{SQL} (intermediate)
	\item[--] Web development: \textcolor{blue}{HTML/CSS} (intermediate), \textcolor{blue}{JavaScript} (intermediate)
	\item[--] Document preparation: \textcolor{blue}{RMarkdown} (advanced), \textcolor{blue}{xaringan} (advanced), \textcolor{blue}{\LaTeX{}} (intermediate)
	%Miscellaneous: \textcolor{blue}{Git/GitHub}, \textcolor{blue}{YAML} 

	\end{itemize}
	
	\item \textcolor{blue}{\textbf{Open-source software development}} (in R; as \textbf{lead developer}; Total downloads: \textcolor{blue}{\textbf{$>$ 500K}}):
	 \vspace*{-0.09in}
	 
	\begin{itemize}
	
	\itemsep-0.1em
	\item[--] \href{https://indrajeetpatil.github.io/ggstatsplot/}{\textcolor{red}{ggstatsplot}} (Downloads: \textcolor{blue}{$>$ 100K}, 2018-): Informative data visualizations with statistical analyses.
	\item[--] \href{https://indrajeetpatil.github.io/groupedstats/}{\textcolor{red}{groupedstats}} (Downloads: \textcolor{blue}{$>$ 70K}, 2018-): Grouped statistical analyses.
	\item[--] \href{https://indrajeetpatil.github.io/groupedstats/}{\textcolor{red}{broomExtra}} (Downloads: \textcolor{blue}{$>$ 90K}, 2019-): Enhancements for working with regression models.
	\item[--] \href{https://indrajeetpatil.github.io/statsExpressions/}{\textcolor{red}{statsExpressions}} (Downloads: \textcolor{blue}{$>$ 70K}, 2019-): Creates expressions with statistical details.
	\item[--] \href{https://indrajeetpatil.github.io/pairwiseComparisons/}{\textcolor{red}{pairwiseComparisons}} (Downloads: \textcolor{blue}{$>$70K}, 2019-): Multiple pairwise comparison tests.
    \item[--] \href{https://indrajeetpatil.github.io/tidyBF/}{\textcolor{red}{tidyBF}} (Downloads: \textcolor{blue}{$>$45K}, 2020-): Tidy wrapper for Bayes Factor tests.
	\item[--] \href{https://indrajeetpatil.github.io/ipmisc/}{\textcolor{red}{ipmisc}} (Downloads: \textcolor{blue}{$>$60K}, 2020-): Miscellaneous functions for data cleaning.	
	\item[--] Co-author on \href{https://easystats.github.io/correlation/}{\textcolor{red}{correlation}}, \href{https://easystats.github.io/insight/}{\textcolor{red}{insight}}, \href{https://easystats.github.io/parameters/}{\textcolor{red}{parameters}}, \href{https://const-ae.github.io/ggsignif/}{\textcolor{red}{ggsignif}}, (downloads: \textcolor{blue}{$>$ 2M})
	
	\end{itemize}

	\item \textcolor{blue}{\textbf{Techniques}}: text mining, meta-analysis, logistic/linear regression, mixed effects regression, clustering \hspace*{0.1in}(\textit{k}-means, hierarchical cluster analysis, linear discriminant analysis), \textit{k}-nearest neighbor, bagging, random \hspace*{0.1in}forests, SVM, dimensionality reduction (PCA, ICA), Reinforcement Learning, Bayesian statistics, cross \hspace*{0.1in}validation, neural networks, Structural Equation Modeling, path analysis
	
	%$\bullet$ \textcolor{blue}{\textbf{GUI softwares}} (for statistical analysis):
	%SPSS, jamovi, JASP, Amos, G*Power
	%\miniskip
	
	%$\bullet$ \textcolor{blue}{\textbf{Online data collection}}: \textcolor{black}{Qualtrics}, \textcolor{black}{MTurk}
    
    \end{itemize}
	%\vspace*{-0.09in}
	
%	$\bullet$ \textcolor{blue}{\textbf{Skin conductance data analysis}}: \textcolor{black}{Ledalab}

	\heading{\textbf{Publications}}
	
	\begin{itemize}
	\item \textbf{\textcolor{red}{13}} first author, peer-reviewed publications\\
	
	\href{https://scholar.google.it/citations?user=kSYuYTUAAAAJ&hl=en&oi=ao}{Citations}: \textbf{\textcolor{red}{767}}, \textit{h}-index: \textbf{\textcolor{red}{12}}, \textit{i}10-index: \textbf{\textcolor{red}{12}}, \href{https://osf.io/hk5f3/}{Open materials} (13/13)\\
	
	Selected media coverage: \href{http://time.com/3242/driving-over-your-best-friend-its-the-right-thing-to-do/}{\textit{Time}}, \href{http://www.huffingtonpost.com/entry/autism-empathy-brain-research_us_56f92575e4b014d3fe237413}{\textit{The Huffington Post}}, \href{http://www.dailymail.co.uk/sciencetech/article-4308284/Virtual-reality-experiment-puts-altruism-test.html}{\textit{Daily Mail}}, \href{http://www.repubblica.it/scienze/2017/04/11/news/area_cervello_perdono-162669836/?rss}{\textit{la Repubblica}}, etc.
	
%\vspace*{-0.09in}
     \end{itemize}

	\heading{\textbf{Education}}
	
	\begin{itemize}	
	
	\itemsep-0.1em
	\item \textbf{\textcolor{blue}{Doctor of Philosophy}} (\textbf{Neuroscience}), \textcolor{black}{SISSA}, Trieste, Italy, 2011-2015 (\textit{summa cum laude}).

	\item \textbf{\textcolor{blue}{Master of Science}} (\textbf{Physics}), Department of Physics, \textcolor{black}{University of Pune}, India, 2008-2010.% (GPA: 4.2/6).
	
	\item \textbf{\textcolor{blue}{Bachelor of Science}} (\textbf{Physics}), \textcolor{black}{Fergusson College}, India, 2005-2008.% (Score: 83$\%$).
%\vspace*{-0.09in}

    \end{itemize}

	\heading{\textbf{Languages}}
	\textbf{Marathi} (C2), \textbf{Hindi} (C2), \textbf{English} (C2), \textbf{German} (B2), \textbf{Italian} (A2)
%\vspace*{-0.09in}
	
	\heading{\textbf{Other Skills}}

	\begin{itemize}	
		
	\item \textcolor{blue}{\textbf{Communication}}: Skilled	at	disseminating complex ideas to a range of audiences, including scientists and the general public (\textgreater ~\textbf{20} talks, published articles for newspapers).	
	
	\item \textcolor{blue}{\textbf{Advising/Project Management}}: Coordinated large teams of multi-national researchers across multiple neuroimaging studies across several years. Supervised and trained \textbf{7} students' undergraduate theses.
	
     \end{itemize}	
	
	\end{document}
